onsetsync: An R Package for Onset Synchrony Analysis

### 2023-01-17 paper/paper.Rmd
Renamed figures

```{r synch2isochron,fig.width=7.0, fig.height=5.0,fig.cap='Onsets arranged for beat sub-divisions for four instruments across the whole piece.'}
fig1 <- plot_by_beat(df = CSS_Song2, 
                     instr = c('Bass','Clave','Guitar','Tres'), 
                     beat = 'SD', 
                     virtual='Isochronous.SD.Time',
                     pcols=2)
print(fig1)
```

@@

```{r, fig.cap='Relative timing deviations from beat sub-divisions across the performance for guitar and tres.'}
print(plot_by_beat(df = CSS_Song2,
  instr = c("Guitar","Tres"),
  beat = "SD",
  virtual = "Isochronous.SD.Time", 
  griddeviations = TRUE))
```

@@

```{r,fig.cap='Asynchronies across multiple instrument pairs.'}
inst <- c("Clave","Bass","Guitar","Tres")
dn <- sync_execute_pairs(CSS_Song2, inst, beat = "SD")
print(plot_by_pair(dn))
```

@@

```{r, fig.cap='Absolute asynchronies between guitar and tres in five performances within the CSS_IEMP dataset.'}
corpus <- onsetsync::CSS_IEMP
D <- sync_sample_paired(corpus,"Guitar","Tres", beat="SD")
D <- D$asynch
D$asynch_abs <- abs(D$asynch)*1000
print(plot_by_dataset(D,"asynch_abs","name", box = TRUE))
```

@@

```{r,fig.cap='Asynchrony between tres and guitar (Y-axis) across time (X-axis) and tempo (illustrated with marker colors).'}
CSS_Song2 <- CSS_Song2 %>%
  group_by(Cycle) %>%
  mutate(Tempo = 240/(max(Isochronous.SD.Time) - 
                        min(Isochronous.SD.Time))) %>%
  ungroup()

@@

```{r periodicityfigure,echo=FALSE,fig.cap='Periodicity analysis of a 5-second extract of guitar playing in Cuban son. Panel A shows the onsets (red) and the conversion into gaussian distributions (blue) for a continuous representation. Panel B displays the difference in onset times as a primitive periodicity measure, Panel C shows the output from autocorrelation function, and Panel D shows the estimation of periodicity by FFT.'}

@@

```{r fourperiodicies, echo=FALSE, fig.cap='Periodicity analysis of four selected instruments in the example song (Palo Alto). The grid lines indicate multiples of the period identified earlier as the underlying beat (217 ms).'}

>>>>

```{r figure1,fig.width=7.0, fig.height=5.0,fig.cap='Onsets arranged for beat sub-divisions for four instruments across the whole piece.'}
fig1 <- plot_by_beat(df = CSS_Song2, 
                     instr = c('Bass','Clave','Guitar','Tres'), 
                     beat = 'SD', 
                     virtual='Isochronous.SD.Time',
                     pcols=2)
print(fig1)
```

@@

```{r figure2, fig.cap='Relative timing deviations from beat sub-divisions across the performance for guitar and tres.'}
print(plot_by_beat(df = CSS_Song2,
  instr = c("Guitar","Tres"),
  beat = "SD",
  virtual = "Isochronous.SD.Time", 
  griddeviations = TRUE))
```

@@

```{r figure3,fig.cap='Asynchronies across multiple instrument pairs.'}
inst <- c("Clave","Bass","Guitar","Tres")
dn <- sync_execute_pairs(CSS_Song2, inst, beat = "SD")
print(plot_by_pair(dn))
```

@@

```{r figure4, fig.cap='Absolute asynchronies between guitar and tres in five performances within the CSS_IEMP dataset.'}
corpus <- onsetsync::CSS_IEMP
D <- sync_sample_paired(corpus,"Guitar","Tres", beat="SD")
D <- D$asynch
D$asynch_abs <- abs(D$asynch)*1000
print(plot_by_dataset(D,"asynch_abs","name", box = TRUE))
```

@@

```{r figure5, fig.cap='Asynchrony between tres and guitar (Y-axis) across time (X-axis) and tempo (illustrated with marker colors).'}
CSS_Song2 <- CSS_Song2 %>%
  group_by(Cycle) %>%
  mutate(Tempo = 240/(max(Isochronous.SD.Time) - 
                        min(Isochronous.SD.Time))) %>%
  ungroup()

@@

```{r figure6, echo=FALSE, fig.cap='Periodicity analysis of a 5-second extract of guitar playing in Cuban son. Panel A shows the onsets (red) and the conversion into gaussian distributions (blue) for a continuous representation. Panel B displays the difference in onset times as a primitive periodicity measure, Panel C shows the output from autocorrelation function, and Panel D shows the estimation of periodicity by FFT.'}

@@

```{r figure7, echo=FALSE, fig.cap='Periodicity analysis of four selected instruments in the example song (Palo Alto). The grid lines indicate multiples of the period identified earlier as the underlying beat (217 ms).'}
